An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-10-06 paper.tex
Fix tables

\begin{table}[!tbp]
\centering
    \begin{tabular}{c||c|c}
        Status & Sent & Received \\
         \hline \hline 
        Before WGC & $67.26\pm99.80$ & $70.11\pm103.37$ \\
        \hline
        After WGC & $77.20\pm102.85$ & $85.90\pm107.38$ \\
        \hline
        Before AD & $218.84\pm226.92$ & $230.50\pm214.75$ \\
        \hline
        After AD & $209.21\pm186.46$ & $219.16\pm189.85$ \\
    \end{tabular}
        \caption{Mean number of emails received for one year before/after becoming a WGC (AD) for the first time. The error is one standard deviation.}
    \label{tab:WGC_email}
\end{table}

@@

\begin{table*}[]
  \small
  \begin{center}
  \begin{tabular}{l|l|l}
  \toprule
    \multirow{2}{*}{Language and influence} 
      & High influence
      & \liwc{bio, we, informal, they, negemo, anger, risk, adjective}  \\ 
    \cmidrule{2-3}
      & Low influence
      & \liwc{sexual, death, ingest, netspeak, health, female, body, affiliation, conj} \\ 
  \hline
    \multirow{2}{*}{Language and role} 
      & WG Chair influence
      & \liwc{tentat, ipron, social, see, feel, we} \\
    \cmidrule{2-3}
      & non-WG Chair
      & \liwc{cogproc, relativ, affiliation, i, reward} \\
  \hline
    \multirow{2}{*}{Changes in Language}
      & Top 10 percentile
      & \liwc{adverb, prep, anger, auxverb, male, cogproc, achiev, risk, focuspresent} \\
    \cmidrule{2-3}
      & Below 50$^{th}$ percentile
      & \liwc{function, ppron, shehe, ipron, number, certain, sexual, informal} \\
  \hline
  \end{tabular}
  \end{center}
  \caption{LIWC categories where $p<0.05$.}
  \label{table:all_results}
\end{table*}

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
      Model & $F_1$ & $\mathit{AUC}$ & $F1_{macro}$ \\
    \midrule
      Most frequent class                & .757   & .500   & .379 \\
      Baseline                           & .758   & .616   & .597 \\
      Baseline + FS                      & .762   & .650   & .610 \\
    \midrule
      Most frequent class                & .724   & .500   & .379 \\
      Baseline                           & .670   & .559   & .547 \\
      Baseline + FS                      & .690   & .620   & .563 \\
      Logistic regression all feats      & .728   & .724   & .666 \\
      Logistic regression all feats + FS & .820   & .822   & .789 \\
      Decision tree all feats + FS       & .822   & .838   & .788 \\
    \bottomrule
  \end{tabular}
  \caption{
    Classifier scores on the entire dataset (251 RFCs, above) and those
    with our features available (155 RFCs), with or without feature
    selection (FS).
  }
  \label{tbl:mlres}
\end{table}

>>>>

\begin{table}[!tbp]
  \centering
  \begin{tabular}{c||c|c}
      Status & Sent & Received \\
       \hline \hline 
      Before WGC & $67.26\pm99.80$ & $70.11\pm103.37$ \\
      \hline
      After WGC & $77.20\pm102.85$ & $85.90\pm107.38$ \\
      \hline
      Before AD & $218.84\pm226.92$ & $230.50\pm214.75$ \\
      \hline
      After AD & $209.21\pm186.46$ & $219.16\pm189.85$ \\
  \end{tabular}
  \caption{
    Mean number of emails received for one year before/after becoming a WGC
    (AD) for the first time. The error is one standard deviation.
  }
  \label{tab:WGC_email}
\end{table}

@@

\begin{table*}
  \centering
  \small
  \begin{tabular}{l|l|l}
  \toprule
    \multirow{2}{*}{Language and influence} 
      & High influence
      & \liwc{bio, we, informal, they, negemo, anger, risk, adjective}  \\ 
    \cmidrule{2-3}
      & Low influence
      & \liwc{sexual, death, ingest, netspeak, health, female, body, affiliation, conj} \\ 
  \hline
    \multirow{2}{*}{Language and role} 
      & WG Chair influence
      & \liwc{tentat, ipron, social, see, feel, we} \\
    \cmidrule{2-3}
      & non-WG Chair
      & \liwc{cogproc, relativ, affiliation, i, reward} \\
  \hline
    \multirow{2}{*}{Changes in Language}
      & Top 10 percentile
      & \liwc{adverb, prep, anger, auxverb, male, cogproc, achiev, risk, focuspresent} \\
    \cmidrule{2-3}
      & Below 50$^{th}$ percentile
      & \liwc{function, ppron, shehe, ipron, number, certain, sexual, informal} \\
  \hline
  \end{tabular}
  \caption{LIWC categories where $p<0.05$.}
  \label{table:all_results}
\end{table*}

@@
